\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-10-05 Code/RankComparison.Rmd

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_dash,
                method = "ds",
                exact = TRUE, B = 500000)
```

>>>>

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_dash,
                method = "ds",
                exact = TRUE, B = 500000)
```
```{r}
old_dash <- read.csv("../Data/Clusrank2019vs2022Dash.csv")
colnames(old_dash) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_dash,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_dash,
                method = "ds",
                exact = TRUE, B = 500000)
```
```{r}
old_women_hurdles <- read.csv("../Data/Clusrank2019vs2022Womens.csv")
colnames(old_women_hurdles) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_women_hurdles,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_women_hurdles,
                method = "ds",
                exact = TRUE, B = 500000)
```
```{r}
old_women_dash <- read.csv("../Data/Clusrank2019vs2022WomensDash.csv")
colnames(old_women_dash) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_women_dash,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_women_dash,
                method = "ds",
                exact = TRUE, B = 500000)
```

### 2024-10-05 Manuscript/reply.tex

\subsection*{To Reviewer}

@@

@@

\begin{comment}
Otherwise, I think the manuscript could be improved by streamlining the
presentation of the organizing material like the problem statements and theory.
The literature review currently reads like an itemized list of all the relevant
studies; revising to focus on the specific arguments the paper hopes to make
could help improve clarity. As it is, I am not entirely sure if the paper is
specifically trying to test a hypothesis offered by others (e.g. the sensors
were calibrated in some way to lead to faster reaction times) or just present a
general framework for studying track and field down the road. I believe the
former is stronger and of more interest than the latter, so making clear the
purpose would help.

\end{comment}  
The second reviewer shared a similar sentiment about not effectively
presenting ideas so we we made improvements to the introduction section to try
and more clearly present our ideas.  We shortened the literature review to only
cite papers that were actually of interest to the paper and tried to clearly
define the two purposes of the paper: to decide of 0.1 seconds is fair, and to
identify inconsistensies with the 2022 reaction times. We try to be precise in
our language as we do not have enough evidence to conclude that the sensors were
calibrated differently, or that Seiko (who make the timing devices) is at fault
for the 2022 reaction times being inexplicably faster. Thus we make general
recommendations for World Athletics and note that the reaction times in 2022
were unusually fast with no clear reason.

@@

Thank you for these encouraging words.

@@

\begin{comment}
The paper’s topic is very important, but has significant issues with the writing
quality and statistical rigor. Right now, the manuscript reads more like report
than a paper. The text lacks significant direction, and does not explain the
goals of the study until the 4th page. Even then, “checking for abnormalities”
is very vague.

@@

In terms of the choice of distribution, Brosnan and Harrison used a exponentially
modified gaussian distribution using athletes sex, ruling periods, competition
rounds. The article is now behind a pay wall.

@@

Unfortunately data such as this is not easy to come by.  We found as much as we
could online, but there is simply not enough data to justify a formal analysis
of his reaction times across lower level meets.  Many track and field races do
not record data on reaction times until at the very high level (national
and world championship).  Simply put, reaction times are not heavily researched
and thus the data material in insufficient.

@@

We added additional explanations to address this in the introductions section.

@@

\subsection*{Associate Editor}
\begin{comment}
I encourage you to consider the issues raised by the reviewers carefully. I have
little additional material to add, other than to emphasize the need to
re-organize the manuscript to more clearly identify the key goals of the work at
the start, and to provide a more concise and focused presentation of the key
findings.
\end{comment}

>>>>

\subsection*{To Reviewer 1}

\jy{What is ``the first point?''  Please quote everything from the
  reviewer, including the positive comments.}

@@

\jy{At the end of each reply, we need to state what changes we made to
  the manuscript with their specific locations. The explanation here
  (the exclusion of 200m dash) should be included in the paper as well.}

@@

\begin{comment}
Otherwise, I think the manuscript could be improved by streamlining the
presentation of the organizing material like the problem statements and theory.
The literature review currently reads like an itemized list of all the relevant
studies; revising to focus on the specific arguments the paper hopes to make
could help improve clarity. As it is, I am not entirely sure if the paper is
specifically trying to test a hypothesis offered by others (e.g. the sensors
were calibrated in some way to lead to faster reaction times) or just present a
general framework for studying track and field down the road. I believe the
former is stronger and of more interest than the latter, so making clear the
purpose would help.
\end{comment}

The second reviewer shared a similar sentiment about not effectively
presenting ideas so we we made improvements to the introduction section to try
and more clearly present our ideas.  We shortened the literature review to only
cite papers that were actually of interest to the paper and tried to clearly
define the two purposes of the paper: to decide of 0.1 seconds is fair, and to
\jy{The order is reversed in the paper.}
identify inconsistensies with the 2022 reaction times. We try to be precise in
our language as we do not have enough evidence to conclude that the sensors were
calibrated differently, or that Seiko (who make the timing devices) is at fault
for the 2022 reaction times being inexplicably faster. Thus we make general
recommendations for World Athletics and note that the reaction times in 2022
were unusually fast with no clear reason.

@@

Thank you for these encouraging words. \jy{State what expansions we
  have done.}

@@

\begin{comment}
The paper’s topic is very important, but has significant issues with the writing
quality and statistical rigor. Right now, the manuscript reads more like report
than a paper. The text lacks significant direction, and does not explain the
goals of the study until the 4th page. Even then, “checking for abnormalities”
is very vague.
\end{comment}

@@

In terms of the choice of distribution, Brosnan and Harrison used a exponentially
modified gaussian distribution using athletes sex, ruling periods, competition
rounds. The article is now behind a pay wall.
\jy{Not a reason for not citing it. We can still find pdf online.}

\jy{Using log-normal distribution for the reaction times is quite easy
  to do. You just take log of the reaction times, and then model them
  in a GLMM with Guassian family. I think we did this, and decided it
  was not good perhaps from the residual qq plots. Please find them
  and add a discussion into the paper.}

\jy{This references has been cited 31 times. Some of these are closely
  related to our topic and should be cited as appropriate.}

@@

Unfortunately data such as this is not easy to come by.  We found as much as we
could online, but there is simply not enough data to justify a formal analysis
of his reaction times across lower level meets.  Many track and field races do
not record data on reaction times until at the very high level (national
and world championship).  Simply put, reaction times are not heavily researched
and thus the data material in insufficient.
\jy{We have added a discussion in paragraph ??? of the Discussion Section.}

\jy{Every point we cannot answer needs to have some response reflected
  in discussions in the manuscript.}

@@

We added additional explanations to address this in the introductions section.
\jy{Give paragraph number for specific locations}

@@

\subsection*{Associate Editor}
\jy{Put this section before the reviewers.}

\begin{comment}
I encourage you to consider the issues raised by the reviewers carefully. I have
little additional material to add, other than to emphasize the need to
re-organize the manuscript to more clearly identify the key goals of the work at
the start, and to provide a more concise and focused presentation of the key
findings.
\end{comment}
